{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-06 Paper/main.tex
Proof

	where the $c(t,s)$ are \textit{Hilbert-Schmidt Kernels} defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be a \textit{Hilberst-Shmidt operator} on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by

@@

	\subsection{Theorem (Karhunen-Lo\'{e}ve expansion)} \label{Proof2}
	Let $X : [0,1]  \rightarrow \mathbb{R}$ be a mean-square continuous stochastic process with $X \in \mathbb{L}^{2}[0,1]$. Then there exists a basis ${\xi^m}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
	\begin{equation}
		X(t) = \mu(t) + \sum_{m=1}^{\infty} \xi^m \nu^m(t),
	\end{equation}
	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi^m$ are given by $\int_{0}^{1} (X(t) - \mu(t)) \nu^m(t)dt$. These coefficients satisfy the following conditions.
	\begin{enumerate}
		\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
		\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = \delta^{m,n}\lambda^m$ %if $m \neq n$
		\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
	\end{enumerate}
	\begin{proof}
		We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator. With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering
		\begin{equation}
			\epsilon_{N}(t) := \mathbb{E} \left[\bigg( X(t) -\mu(t)- \sum_{m=1}^{N} \xi^m \nu^m(t)\bigg)^2 \right]
			= \mathbb{E} \left[\bigg( F(t) - \sum_{m=1}^{N} \xi^m \nu^m(t)\bigg)^2 \right]
		\end{equation}
		where $F(t)$ is the centered process of $X(t)$.
		Once it is shown that $\lim\limits_{N \rightarrow \infty} \epsilon_{N}(t) = 0$ uniformly in [0,1], the proof is completed.
		\begin{equation}\label{Thr1}
			\begin{split}
				\epsilon_{N}(t) = &\mathbb{E} \left[\bigg( F(t) - \sum_{m=1}^{N} \xi^m 	\nu^m(t)\bigg)^2 \right]\\
				= & \mathbb{E}[F(t)^{2}] - 2\mathbb{E}\bigg[F(t)\sum_{m=1}^{N}\xi^m\nu^m(t)\bigg] + \mathbb{E}\bigg[\sum_{m=1}^{N}\sum_{n=1}^{N}\xi^m\xi^n\nu^m(t)\nu^n(t)\bigg]
			\end{split}
		\end{equation}

		Here, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (\ref{CovarianceFunction}) since F(t) is the centered process. Now, take the second term
		\begin{equation}\label{Thr2}
			\begin{split}
				\mathbb{E} \bigg[ F(t) \sum_{m=1}^{N} {\color{red}\xi^m}\nu^m(t) \bigg] = & \mathbb{E} \left[ F(t) \sum_{m=1}^{N} {\color{red}\bigg(\int_{0}^{1} F(s)\nu^m(s)ds\bigg)} \nu^m(t) \right]\\
				= & \mathbb{E} \left[ \sum_{m=1}^{N} \bigg(\int_{0}^{1} F(t)F(s)\nu^m(s)ds\bigg) \nu^m(t) \right]\\
				= & \sum_{m=1}^{N} \bigg(\int_{0}^{1} {\color{blue}\mathbb{E}[F(t)F(s)]}\nu^m(s)ds\bigg)\nu^m(t)\\
				= & \sum_{m=1}^{N} {\color{teal}\bigg(\int_{0}^{1} {\color{blue}c(t,s)} \nu^m(s)ds\bigg)}\nu^m(t)\\
				= & \sum_{m=1}^{N}{\color{teal}[K\nu^m](t)}\nu^m(t) \\
				= &\sum_{m=1}^{N}{\color{teal}\lambda^m\nu^m(t)}\nu^m(t) = \sum_{m=1}^{N}\lambda^m\nu^m(t)^{2}
			\end{split}
		\end{equation}

>>>>

	where the $c(t,s)$ are Hilbert-Schmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be a Hilberst-Shmidt operator on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by

@@

	\subsection{Theorem (Karhunen-Lo\'{e}ve expansion)} \label{Proof2}
	Let $X : [0,1]  \rightarrow \mathbb{R}$ be a mean-square continuous stochastic process, namely, $\lim\limits_{\epsilon \rightarrow 0} \mathbb{E}[(X(t+\epsilon) - X(t))^2]$ = 0, such that $X \in \mathbb{L}^{2}[0,1]$. Then there exists a basis ${\xi^m}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
	\begin{equation}
		X(t) = \mu(t) + \sum_{m=1}^{\infty} \xi^m \nu^m(t),
	\end{equation}
	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi^m$ are given by $\int_{0}^{1} (X(t) - \mu(t)) \nu^m(t)dt$. These coefficients satisfy the following conditions.
	\begin{enumerate}
		\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
		\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = \delta^{m,n}\lambda^m$ %if $m \neq n$
		\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
	\end{enumerate}
	\begin{proof}
		Let $K$ be a Hilbert-Schmidt operator as in \ref{HSKernal}.We know that $K$ has a complete set of eigenfunctions ${\nu^m}$ in $\mathbb{L}^{2}[0,1]$  and non-negative eigenvalues $\lambda^m$ since $K$ is a positive compact self-adjoint operator. With the reminder that $\xi^m$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering
		\begin{equation}
			\epsilon_{N}(t) := \mathbb{E} \left[\bigg( X(t) -\mu(t)- \sum_{m=1}^{N} \xi^m \nu^m(t)\bigg)^2 \right]
			= \mathbb{E} \left[\bigg( F(t) - \sum_{m=1}^{N} \xi^m \nu^m(t)\bigg)^2 \right]
		\end{equation}
		where $F(t)$ is the centered process of $X(t)$.
		Once it is shown that $\lim\limits_{N \rightarrow \infty} \epsilon_{N}(t) = 0$ uniformly in [0,1], the proof is completed.
		\begin{equation}\label{Thr1}
			\begin{split}
				\epsilon_{N}(t) = &\mathbb{E} \left[\bigg( F(t) - \sum_{m=1}^{N} \xi^m 	\nu^m(t)\bigg)^2 \right]\\
				= & \mathbb{E}[F(t)^{2}] - 2\mathbb{E}\bigg[F(t)\sum_{m=1}^{N}\xi^m\nu^m(t)\bigg] + \mathbb{E}\bigg[\sum_{m=1}^{N}\sum_{n=1}^{N}\xi^m\xi^n\nu^m(t)\nu^n(t)\bigg]
			\end{split}
		\end{equation}

		Here, $\mathbb{E}[F(t)^{2}] = c(t,t)$ as in (\ref{CovarianceFunction}) since $F(t)$ is the centered process. Now, take the second term
		\begin{equation}\label{Thr2}
			\begin{split}
				\mathbb{E} \bigg[ F(t) \sum_{m=1}^{N} {\color{red}\xi^m}\nu^m(t) \bigg] = & \mathbb{E} \left[ F(t) \sum_{m=1}^{N} {\color{red}\bigg(\int_{0}^{1} F(s)\nu^m(s)ds\bigg)} \nu^m(t) \right]\\
				= & \mathbb{E} \left[ \sum_{m=1}^{N} \bigg(\int_{0}^{1} F(t)F(s)\nu^m(s)ds\bigg) \nu^m(t) \right]\\
				= & \sum_{m=1}^{N} \bigg(\int_{0}^{1} {\color{blue}\mathbb{E}[F(t)F(s)]}\nu^m(s)ds\bigg)\nu^m(t)\\
				= & \sum_{m=1}^{N} {\color{teal}\bigg(\int_{0}^{1} {\color{blue}c(t,s)} \nu^m(s)ds\bigg)}\nu^m(t)\\
				= & \sum_{m=1}^{N}{\color{teal}[K\nu^m](t)}\nu^m(t) \\
				= &\sum_{m=1}^{N}{\color{teal}\lambda^m\nu^m(t)}\nu^m(t) = \sum_{m=1}^{N}\lambda^m\nu^m(t)^{2}
			\end{split}
		\end{equation}
